Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-31 Manuscript.Rmd
frontpage

Corresponding authors: Alexandra G. Mitchell (agmitchell@cfin.au.dk) and Francesca Fardo (francesca@cfin.au.dk)

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes. Within dermatomes, the relative location of the cold thermode was proximal or distal. Across dermatomes, the relative location of the corresponding spinal segments was rostral or caudal. "}
ggdraw() +
    draw_image(magick::image_read(here::here("figures","figure1.PNG")), scale = 1)
```

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = " Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning). Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes. Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals. A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning). A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce. Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning). A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce. Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}

@@

# Supplementary material
```{r,warning = F, message = F, echo = F}
get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

>>>>

Corresponding authors: Alexandra G. Mitchell ([agmitchell\@cfin.au.dk](mailto:agmitchell@cfin.au.dk){.email}) and Francesca Fardo ([francesca\@cfin.au.dk](mailto:francesca@cfin.au.dk){.email})

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 1) Four experimental conditions depicting an exemplar cold and warm thermode placement within and across dermatomes. Within dermatomes, the relative location of the cold thermode was proximal or distal. Across dermatomes, the relative location of the corresponding spinal segments was rostral or caudal. "}
ggdraw() +
    draw_image(magick::image_read(here::here("figures","figure1.PNG")), scale = 1)
```

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 2) Difference in VAS ratings between within and across dermatome conditions for each type of stimulation (Non-TGI and TGI) in each VAS rating quality (cold, warm and burning). Positive values represent higher ratings within dermatomes, negative values represent higher ratings across dermatomes. Small dots are individual subject means, large dots are population means for each condition and error bars are 95% confidence intervals. A) first experiment with the cold thermode as the reference, and B second experiment with the warm thermode as referece."}

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 3) Difference in VAS ratings between the proximal and distal dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning). A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce. Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}

@@

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure 4) Difference in VAS ratings between the Caudal and Rostral dermatome conditions and  the stimulation type (Non-TGI, TGI) for all VAS rating types (Cold, warm, Burning). A, first experiment with the cold  thermode as the reference, and B with the warm thermode as referce. Small points show data from each participant, large dots are means across trials for each condition, and error bars show 95% confidence intervals."}

@@

# Supplementary material

```{r,warning = F, message = F, echo = F}
get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")
